\bf\mftitle

### 2011-01-24 doc/jInfer/base/base.tex
Documentation: BasicIGG module.

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer: & vektor \\ \hline
Required tokens:       & none \\ \hline
Provided tokens:       & none \\ \hline
Module dependencies:   & none \\ \hline
Public packages:       & cz.cuni.mff.ksi.jinfer.base.automaton \newline
cz.cuni.mff.ksi.jinfer.base.interfaces \newline
cz.cuni.mff.ksi.jinfer.base.interfaces.inference \newline
cz.cuni.mff.ksi.jinfer.base.interfaces.nodes \newline
cz.cuni.mff.ksi.jinfer.base.objects \newline
cz.cuni.mff.ksi.jinfer.base.objects.nodes \newline
cz.cuni.mff.ksi.jinfer.base.regexp \newline
cz.cuni.mff.ksi.jinfer.base.utils \newline
org.apache.log4j.* \\ \hline
\end{tabular}

>>>>

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer: & Matej Vitásek \\ \hline
Required tokens:       & none \\ \hline
Provided tokens:       & none \\ \hline
Module dependencies:   & none \\ \hline
Public packages:       & cz.cuni.mff.ksi.jinfer.base.automaton \newline
cz.cuni.mff.ksi.jinfer.base.interfaces \newline
cz.cuni.mff.ksi.jinfer.base.interfaces.inference \newline
cz.cuni.mff.ksi.jinfer.base.interfaces.nodes \newline
cz.cuni.mff.ksi.jinfer.base.objects \newline
cz.cuni.mff.ksi.jinfer.base.objects.nodes \newline
cz.cuni.mff.ksi.jinfer.base.regexp \newline
cz.cuni.mff.ksi.jinfer.base.utils \newline
org.apache.log4j.* \\ \hline
\end{tabular}
